\documentclass[]{clean-resume}

\begin{document}

\newcommand{\address}{2466 N Oakland Ave. \#320 Milwaukee, WI 53211}
\newcommand{\phone}{(608) 358-3489}
\newcommand{\email}{\href{mailto:tkhunlertkit@gmail.com?subject=Resume}{tkhunlertkit@gmail.com}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%% Title %%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\header{Tanawat Khunlertkit}{Software Engineer}{\phone $~\cdot~$ \email}

\section{Core Competencies}

Go $\cdot$
Python $\cdot$
Java $\cdot$
C $\cdot$
C++ $\cdot$
SQL $\cdot$
JavaScript \\
%
ARM7TDMI $\cdot$ 
MIPS $\cdot$
Verilog $\cdot$
Quartus \\
%
Redis$\cdot$
Docker $\cdot$
Git \\
%
English $\cdot$
Thai

\section{Work History}

\entry
	{Mitel Networks Corporation}
	{}
	{Summer 2018}
	{Milwaukee, WI}
	{
		Developed Internet Of Things platform as a service. The platform allows users to create a network of devices that send data to the server and sends alerts if the reading values exceed a certain threshold. My prinmary contributions include analysis rules platform that can be configured by the user for devices to be evaluated when the server received the data. 
	}

\entry
{College for Teens/College for Kids Program}
{University of Wisconsin - Milwaukee}
{Summer 2014}
{Milwaukee, WI}
{
	Develop and teach courses related to computer programming designed for high school students. Courses include:
	\vspace{-5pt}
	\begin{itemize} \itemsep -5pt
		\item {\sl Create Your Own Computer Games}: creation of Pong and Alien Invasion using Visual Basic.
		\item {\sl Programming Language}: Basic syntax and logic for programming in Java
		\item {\sl Design Your Web page}: Using Dream weaver and HTML to create a simple web page.
	\end{itemize}
}

\entry
	{Project Assistant}
	{University of Wisconsin-Madison}
	{Summer 2007}
	{Milwaukee, WI}
	{
		Developed a Java program of Monte Carlo Simulation to identify optimal joint fixtures for automotive assembly line.		
	}

\section{Education}

\entry
	{PhD Computer Science}
	{University of Wisconsin - Milwaukee}
	{2013 - 2019}
	{Milwaukee, WI}
	{
		\emph{Quality of Life Prediction}: Using patient database for statistical analysis in order to predict the length of hospital stays and the probability of readmission within 30 days of discharged based on the current condition of the individual patient.
	}

\entry
	{MS Computer Science}
	{University of Wisconsin - Milwaukee}
	{2010 - 2012}
	{Milwaukee, WI}
	{
		\emph{Security Protocols on Vehicle-to-Vehicle Communication}: Implementation and timing comparison between Elliptic Curve Cryptography and Advanced Encryption Standard.
	}

\entry
	{BS Computer Engineering and Computer Science}
	{University of Wisconsin - Madison}
	{2007 - 2009}
	{Madison, WI}
	{
		\emph{Senior Project}: Stepper Motor Controller Design and written in Verilog. Implemented on 
		ARM-FPGA board, to be used as the basis for a wirelessly controlled turret.
	}

\section{Teaching History}

\entry
	{University of Wisconsin - Milwaukee}
	{}
	{2010 - Now}
	{Milwaukee, WI}
	{
		Plan and develop curriculum for lab sessions of Software Engineering, intermediate programming using Java, and client-side application development. Grader for additional five courses including computer architecture, computer networks, algorithm design and analysis, and operating systems.
	}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%  Academic Experience %%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Academic Experience}
%\begin{longtable}{lp{14cm}}
%%Current & \textbf{Ph.D. Dissertation}\\
%%        & Prediction of Patients health progression using Neural Networks and 
%%          Markov Chains.\\
%Spring 2015 & \textbf{Neural Network and Brain Modeling}\\
%            & Using Neural Networks and the concept of Principle Component Analysis 
%              as a machine learning algorithm to recognize digital hand-written 
%              numberics.\\
%Spring 2013 & \textbf{Information and Coding Theory}\\
%            & Implementation of Huffman Coding Compression based on the given text 
%              input written in Java.\\
%Fall 2012 & \textbf{Android Programming}\\
%          & Programming android device to work with micro controller via Bluetooth. 
%            Commands include reading the potentiometer and reading the temperature 
%            on the embedded system written in C.\\
%Spring 2011 & \textbf{Computer Networks Laboratory}\\
%            & Asterisk phone server on Linux router using Session Initiation 
%              Protocol (SIP).\\
%Fall 2010 & \textbf{Software Engineering}\\
%          & Music Player in Java. Features include drag-and-drop play list 
%            from a text file.\\
%Spring 2009 & \textbf{Embedded System Design}\\
%            & Stepper Motor Controller Design written in Verilog, Implemented on 
%              ARM-FPGA board, to be integrated with other components.\\
%Spring 2009 & \textbf{Intro to database Management System}\\
%            & Design Back-end for a Simple Database System written in C++.\\
%Fall 2008 & \textbf{Digital Design and Synthesis}\\
%          & Design Calibrated Temperature Integrated Circuit using Verilog and 
%            Synthesize with Synopsys.\\
%Fall 2008 & \textbf{Intro to Programming Languages and Compilers}\\
%          & Conversion from high level programming language (C) to Assembly 
%            language (MIPS).\\
%Spring 2008 & \textbf{Introduction to Operating Systems}\\
%            & Simulator for comparison of CPU Scheduling Algorithms (Clairvoyance 
%              and Priority Queue) written in C.\\
%Fall 2007 & \textbf{Introduction to Computer Architecture}\\
%          & Design a 16-bit Microprocessor with 16 instructions set written in 
%            Quartus.
%\end{longtable}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%% Scope of Excellence %%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Scope of Excellence}
%\noindent \begin{longtable}{lp{15cm}}
%\textit{Computer Languages:} & Python, Java, C, C++, HTML and CSS, SQL, Go, MATLAB.\\
%\textit{Assembly Language:}  & ARM7TDMI, MIPS. \\
%\textit{Hardware Language:}  & Verilog, Quartus. \\
%\textit{Operating Systems:}  & Windows, Linux, Mac OS. \\
%\textit{Languages:}          & English (Fluent) and Thai (Fluent).\\
%\end{longtable}

\end{document}
