\documentclass[11pt]{article}
\usepackage[top=0.6in,left=1in,right=1in,bottom=0.7in]{geometry}
\usepackage{hyperref}
\usepackage{titlesec}
\usepackage{bold-extra}
\usepackage{longtable}
\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{emptypage}
\usepackage[usenames, dvipsnames]{color}

%%%%% Parameter Setup %%%%%%%
\definecolor{mygray}{gray}{0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=blue, linkcolor=blue}
\titleformat{\section}{\large\scshape\bfseries\raggedright\vspace{0.25em}}{}{0em}{}[\titlerule\vspace{-0.5em}]
\titlespacing{\section}{0pt}{3pt}{3pt}
\pagestyle{fancy}
\fancyhf{}
\rfoot{\thepage~\textbar~\color{mygray}\scshape Page}

\renewcommand{\headrulewidth}{0pt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Begin Document %%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%% Title %%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
{\LARGE \textbf{Tanawat Khunlertkit}}\\
(608) 358-3489 \\
\href{mailto:tkhunlertkit@gmail.com}{tkhunlertkit@gmail.com}\\

\end{center}
\vspace{-1.5em}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%% Objective %%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\section{Objective}
%\vspace{1em}
%A position in the field of computer programming and machine learning with special interests in medical applications.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%% EDUCATION %%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education}
\vspace{1em}
%%%%% Ph.D. %%%%%
\noindent \textbf{University of Wisconsin-Milwaukee}, Milwaukee, WI\\
\indent \textbf{Ph.D. Computer Science} \\
\indent \begin{tabular}{l p{11cm}}
\textit{Date of Graduation:}    & Expected May 2019\\
\textit{Dissertation Thesis:} & Using patient database for statistical analysis 
                                in order to predict the length of hospital stays of the 
                                individual patient based on the current condition\\
\end{tabular}
\\\\
%%%%% MS %%%%%
\noindent \textbf{University of Wisconsin-Milwaukee}, Milwaukee, WI\\
\indent \textbf{Master of Science in Computer Science} \\
\indent \begin{tabular}{l p{11cm}}
\textit{Date of Graduation:} & December 2012\\
\textit{Research Objective:} & Implementation of security protocols on Vehicle-to-Vehicle Communication. Timing comparison between Elliptic Curve Cryptography and Advanced Encryption Standard. \\
\end{tabular}
\\\\
%%%%% BS %%%%%
\noindent \textbf{University of Wisconsin-Madison}, Madison, WI\\
\indent \textbf{Bachelor of Science in Computer Engineering and Computer Science} \\
\indent \begin{tabular}{l p{11cm}}
\textit{Date of Graduation:} & December 2009\\
\end{tabular}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%% Work Experience %%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Work Experinece}

%%%%%%%%%%% TA %%%%%%%%%%%%%%%%
\noindent \begin{longtable}{l p{14cm}}
	Summer 2018 & \textbf{Software Developer}\\
			  	& ~~~\textbf{Mitel Networks Corporation}\\
			  	&
Developed 

\noindent \begin{longtable}{l p{14cm}}
Fall 2012 & \textbf{Teaching Assistant}\\
- Present & ~~~\textbf{University of Wisconsin-Milwaukee}\\
          &
  %%%% Details of TA %%%%%%%           
Plan and develop curriculum, along with other teaching materials, for lab sessions.  Supervise graduate students on semester projects. Classes include:
\vspace{-1em}
\begin{itemize} \itemsep -5pt % Reduce space between items
\item {\sl Software Engineering (Spring 2014 - Present)}: Develop weekly activities for students and supervise students on Software Design Pattern.
\item {\sl Intermediate Computer Programming (Fall 2013)}: Based on Java programming language using classes, inheritance, exceptions, and simple Graphical User Interface.
\item {\sl Introductory to Computer Programming (Fall 2012 - Spring 2013)}: Basic Concepts of programming languages.
\item {\sl Introduction to Web Document Production (Spring 2013)}: HTML and CSS. 
\vspace*{-\baselineskip}
\end{itemize}\\

%%%%%%%%%%% CFT/CFK %%%%%%%%%%%%%%
Summer & \textbf{College for Teens/College for Kids Program}\\
2014   & ~~~\textbf{University of Wisconsin-Milwaukee}\\
	   &
    %%%%%% Details of CFT / CFK %%%%%%%%%
Develop and teach courses related to computer programming design for high school students. Courses include:
\vspace{-1em}
\begin{itemize} \itemsep -2pt
        \item {\sl Create Your Own Computer Games}: creation of Pong and Alien Invasion using Visual Basic.
        \item {\sl Programming Language}: Basic syntax and logic for programming in Java
\item {\sl Design Your Web page}: Using the mixture of Dream weaver and HTML to create a simple web page.
\vspace*{-\baselineskip}
\end{itemize} \\

%%%%%%%%%% Project Assistant %%%%%%%%%%%
Summer & \textbf{Project Assistant} \\
2007   & ~~~\textbf{University of Wisconsin-Madison}\\
       & Java programing of Monte Carlo Simulation to identify optimal joint fixtures for automotive assembly line.
\end{longtable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%% Awards and Achievements %%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
\section{Academic Achievements}
\noindent \begin{longtable}{lp{13.5cm}}
Spring 2013   & \textbf{CEAS Dean's Scholarship}\\
- Spring 2015 & Scholarships are given to assist CEAS faculty in recruiting 
                talented students by offering multi-year support to new 
                exceptional graduate students.\\
Fall 2011  & \textbf{Chancellor's Graduate Student Awards}\\
           & Awards are given to one of the best students who shows great 
             potential.
\end{longtable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%  Academic Experience %%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Academic Experience}
\begin{longtable}{lp{14cm}}
%Current & \textbf{Ph.D. Dissertation}\\
%        & Prediction of Patients health progression using Neural Networks and 
%          Markov Chains.\\
Spring 2015 & \textbf{Neural Network and Brain Modeling}\\
            & Using Neural Networks and the concept of Principle Component Analysis 
              as a machine learning algorithm to recognize digital hand-written 
              numberics.\\
Spring 2013 & \textbf{Information and Coding Theory}\\
            & Implementation of Huffman Coding Compression based on the given text 
              input written in Java.\\
Fall 2012 & \textbf{Android Programming}\\
          & Programming android device to work with micro controller via Bluetooth. 
            Commands include reading the potentiometer and reading the temperature 
            on the embedded system written in C.\\
Spring 2011 & \textbf{Computer Networks Laboratory}\\
            & Asterisk phone server on Linux router using Session Initiation 
              Protocol (SIP).\\
Fall 2010 & \textbf{Software Engineering}\\
          & Music Player in Java. Features include drag-and-drop play list 
            from a text file.\\
Spring 2009 & \textbf{Embedded System Design}\\
            & Stepper Motor Controller Design written in Verilog, Implemented on 
              ARM-FPGA board, to be integrated with other components.\\
Spring 2009 & \textbf{Intro to database Management System}\\
            & Design Back-end for a Simple Database System written in C++.\\
Fall 2008 & \textbf{Digital Design and Synthesis}\\
          & Design Calibrated Temperature Integrated Circuit using Verilog and 
            Synthesize with Synopsys.\\
Fall 2008 & \textbf{Intro to Programming Languages and Compilers}\\
          & Conversion from high level programming language (C) to Assembly 
            language (MIPS).\\
Spring 2008 & \textbf{Introduction to Operating Systems}\\
            & Simulator for comparison of CPU Scheduling Algorithms (Clairvoyance 
              and Priority Queue) written in C.\\
Fall 2007 & \textbf{Introduction to Computer Architecture}\\
          & Design a 16-bit Microprocessor with 16 instructions set written in 
            Quartus.
\end{longtable}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%% Scope of Excellence %%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Scope of Excellence}
\noindent \begin{longtable}{lp{15cm}}
\textit{Computer Languages:} & Python, Java, C, C++, HTML and CSS, SQL, Go, MATLAB.\\
\textit{Assembly Language:}  & ARM7TDMI, MIPS. \\
\textit{Hardware Language:}  & Verilog, Quartus. \\
\textit{Operating Systems:}  & Windows, Linux, Mac OS. \\
\textit{Languages:}          & English (Fluent) and Thai (Fluent).\\
\end{longtable}

\end{document}
